Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-12 paper/paper.tex
pass on intro

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
automates test generation in scenarios where multiple implementations
of a system exist. It leverages the diversity across system's
implementations to detect anomalous behavior.
%% WHAT WE DID
This paper reports the results of a study we conducted to assess the
ability of DT to find bugs on \js{} engines.  We analyzed
the impact of two orthogonal dimensions: test mining and fuzzing. The
first dimension, test mining, considers the effect that \js{} test
files mined from the repository of a given open-source engine have in
detecting functional bugs in other engines. The second dimension,
fuzzing, considers the impact of fuzzing the mined files in bug
detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

>>>>

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior.
%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT for bug finding. More
precisely, we analyzed the impact of two orthogonal factors in the use
of DT: test mining and fuzzing. The first dimension, test mining,
considers the effect that \js{} test files mined from the repository
of a given open-source engine have in detecting functional bugs in
other engines. The second dimension, fuzzing, considers the impact of
fuzzing the mined files in bug detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}
